Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit mden profile result 1

    As mentioned above, our current SMF is subject to an additional 20\% uncertainty 
    that will be addressed in forthcoming work. 
    Hence, we do not attempt a detailed comparison with respect to previous works on 
    the SMF, reserving this for a future study. 
    Here, we simply note that the HSC SMF derived using \mtot{} is close to the one 
    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming 
    the \texttt{SerExp} models.  
    Our sample and the \citet{Bernardi2017} sample have different redshifts. 
    Without a more in-depth study, we cannot ascertain whether or not the apparent 
    agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
    lack of evolution in the galaxy SMF, or that other effects are at play 
    (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled
    redshift evolution.  
    In future work, it will be interesting to perform a more consistent analysis to 
    search for redshift evolution in the galaxy SMF and to study whether or not 
    massive galaxies in HSC are well described by \texttt{SerExp} models.

@@

       From Figure~\ref{fig:avg_prof} we can see  the galaxies in our sample have homogeneous profiles on small radial scales. The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope of  \mden{} remains similar.  From previous work on this topic, we already know that the inner regions of massive elliptical galaxies display relatively uniform structural (e.g. \mden{} profile, isophotal shape, 
    \citealt{Lauer07, Kormendy2009, Schombert2015} and kinematic (e.g. 
    \citealt{Cappellari13b}) properties.  However,  Figure~\ref{fig:avg_prof} reveals  a significant diversity in the outer envelopes of massive galaxies.  Given the \s2n{} of HSC images at these surface brightness levels, the scatter shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in the stellar envelopes of massive galaxies.}. Importantly, Figure~\ref{fig:avg_prof} shows that the global mass profiles of galaxies at these masses are  \textbf{clearly not 
    self-similar} out to 100 kpc.

In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our 
\mden{} profiles with results from previous  work. Deep \mden{} profiles of massive galaxies are rarely available. Even in the nearby universe, it is not trivial to map the low surface brightness  outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). There are also not many galaxies that are this massive in the local universe. For example, the central galaxy of the COMA cluster, NCG xxx has a galaxy mass of xxxx and is smaller than any of the galaxies considered in this sample.

Most previous studies have often focused on surface brightness profiles instead of mass density profiles.  Results can also depend on the stacking technique or the model  used to extract the profile (e.g., \citealt{Tal2011, DSouza2015}). \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively shallow 
    images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).  This sample is a very low redshift ($z=xxx$), and so the \citet{Huang2013a} galaxies are accurate to  smaller scales (down to $r=1$ kpc) than our HSC sample.  Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc). CGS images are deeper than SDSS images in the $r$-band, but the median 
    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

>>>>

    As mentioned above, our current SMF is subject to an additional 20\% uncertainty 
    that will be addressed in forthcoming work. 
    Hence, we do not attempt a detailed comparison with respect to previous works on 
    the SMF, reserving this for a future study. 
    Here, we simply note that the HSC SMF derived using \mtot{} is close to the one 
    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming 
    the \texttt{SerExp} models.  
    Our sample and the \citet{Bernardi2017} sample have different redshifts. 
    Without a more in-depth study, we cannot ascertain whether or not the apparent 
    agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
    lack of evolution in the galaxy SMF, or that other effects are at play 
    (for example, the difference between \mtot{} masses and \texttt{SerExp} masses) 
    that have cancelled redshift evolution.  
    In future work, it will be interesting to perform a more consistent analysis to 
    search for redshift evolution in the galaxy SMF and to study whether or not 
    massive galaxies in HSC are well described by \texttt{SerExp} models.

@@

    From Figure~\ref{fig:avg_prof} we can see the galaxies in our sample have 
    homogeneous profiles on small radial scales. 
    The amplitude of \mden{} increases with galaxy mass on 10 kpc scales but the slope 
    of \mden{} remains similar.  
    From previous work on this topic, we already know that the inner regions of 
    massive elliptical galaxies display relatively uniform structural (e.g.
    \mden{} profile, isophotal shape: e.g. \citealt{Lauer07, Kormendy2009, 
    Schombert2015}; and kinematic: e.g. \citealt{Cappellari13b}) properties.  
    However, Figure~\ref{fig:avg_prof} reveals a significant diversity in the outer 
    envelopes of massive galaxies.  
    Given the \s2n{} of HSC images at these surface brightness levels, the scatter 
    shown in Figure~\ref{fig:avg_prof} corresponds to \textbf{intrinsic scatter in 
    the stellar envelopes of massive galaxies}. 
    Importantly, Figure~\ref{fig:avg_prof} shows that the global \mden{} profiles 
    of galaxies at these masses are \textbf{clearly not self-similar} out to 100 
    kpc and have outskirts with larger scatter.

    In the right-hand side of Fig.~\ref{fig:avg_prof}, we compare our \mden{} 
    profiles with results from previous work. 
    Deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is not trivial to map the low surface
    brightness outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
    The number of very massive galaxies is also very limited in the local universe.
    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
    luminosity) within 108 Mpc.

    Most previous studies have often focused on surface brightness profiles instead 
    of mass density profiles.  
    Results can also depend on the stacking technique or the model used to extract 
    the profile (e.g., \citealt{Tal2011, DSouza2015}). 
    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$) based on relatively 
    shallow images from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}).  
    This sample is at very low redshift ($z<0.02$), and so the \mden{} profiles from 
    \citet{Huang2013a} galaxies are accurate to smaller scales (down to $r=1$ kpc) 
    than our HSC ones.  
    Our \mden{} profiles show good agreement with the \citet{Huang2013a} sample in the radial range of overlap (out to 50 kpc). CGS images are deeper than SDSS images in the $r$-band, but the median 
    profiles from \citet{Huang2013a} still only reach to ${\sim} 50$ kpc for $z{\sim} 0$ (PUT THE EXACT REDSHIFTS HERE)
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
